Concrete Semantics for Pushdown Analysis:\\The Essence of Summarization

### 2013-05-06 paper.tex
Made System definition prettier.
Fixed bad definition of S'
Slight correction to F'

To turn this semantics into PDCFA's algorithm for constructing a Dyck
state graph, we apply a widening operator to make $\mstore$, $\mkont$,
and $\mmemo$ shared amongst all states. Further techniques for a
performant implementation can be found in
\citet{ianjohnson:oaam:2013}.

\begin{align*}
  \mastate \in \sa{State} &= \Expr \times \Env \times \Kont \\
  \System &= \wp(\sa{State} \times \Store) \times \wp{\sa{State}} \times \Store \times (\Expr \times \Env \times \Store \to \wp(\Kont)) \times (\Expr \times \Env \times \Store \to \wp{\Value}) \\
  {\mathcal F} : \System \to \System \\
  {\mathcal F}(S, F, \mstore, \mktab, \mmemo) &= (S \cup S', F', \mstore', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\mastate \in F, \wn(\mastate,\mstore,\mktab,\mmemo) \stepto \mstate'} \\
                S' &= \setbuild{(\mastate',\mstore')}{\wn(\mastate', \mstore', \_, \_) \in I} \\
                F' &= \setbuild{\mastate'}{(\mastate',\_) \in S' \setminus S} \\
                \mstore' &= \bigsqcup\setbuild{\mstore'}{\wn(\_, \mstore',\_,\_) \in I} \\
                \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \_, \mktab', \_) \in I} \\
                \mmemo' &=  \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \_, \mmemo') \in I} \\
                \wn(\tpl{\mexpr,\menv,\mkont},\mstore,\mktab,\mmemo) &= \tpl{(\mexpr,\menv),\mstore,\mkont,\mktab,\mmemo}
\end{align*}

>>>>

To turn this semantics into PDCFA's algorithm for constructing a Dyck
state graph, we apply a widening operator ${\mathcal F}$ to make $\mstore$, $\mkont$,
and $\mmemo$ shared amongst all states. Further techniques for a
performant implementation can be found in
\citet{ianjohnson:oaam:2013}.

\begin{align*}
  \mastate \in \sa{State} &= \Expr \times \Env \times \Kont \\
  \System &= \wp(\sa{State} \times \Store) \times \wp(\sa{State}) \times \Store \times \KTab \times \Memo \\
  {\mathcal F} &: \System \to \System \\
  {\mathcal F}(S, F, \mstore, \mktab, \mmemo) &= (S \cup S', F', \mstore', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\mastate \in F, \wn(\mastate,\mstore,\mktab,\mmemo) \stepto \mstate'} \\
                \mstore' &= \bigsqcup\setbuild{\mstore'}{\wn(\_, \mstore',\_,\_) \in I} \\
                \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \_, \mktab', \_) \in I} \\
                \mmemo' &=  \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \_, \mmemo') \in I} \\
                S' &= \setbuild{(\mastate',\mstore')}{\wn(\mastate', \_, \_, \_) \in I} \\
                F' &= \setbuild{\mastate'}{(\mastate',\_) \in S', (\mastate',\mstore') \notin S} \\
                \wn(\tpl{(\mexpr,\menv),\mkont},\mstore,\mktab,\mmemo) &= \tpl{(\mexpr,\menv),\mstore,\mkont,\mktab,\mmemo}
\end{align*}
